\documentclass{letter}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\begin{center}

\textbf{\Large Statement of Purpose} 

\textbf{\Large of Tasnimul Hasnat}

\end{center}

As a computer science student with a strong passion for cybersecurity, I am writing to express my interest in applying for the Master's degree in cybersecurity at Carnegie Mellon University. I was immediately drawn to the program due to its outstanding reputation in the field and the opportunity to work with leading experts, particularly Professor X. After conducting thorough research on the university's publications, I was thrilled to discover that Professor X's research focuses on the same topics that I am deeply interested in, specifically, automated exploit generation.

Automated exploit generation is a cutting-edge field that involves developing algorithms and tools that can automatically identify and exploit vulnerabilities in software systems. This field has become increasingly important in recent years as the number of cyberattacks continues to rise, and businesses struggle to keep up with the constantly evolving threat landscape. During my undergraduate studies, I had the opportunity to work on a thesis project focused on this field, which sparked my interest in cybersecurity and solidified my desire to pursue advanced studies in this area.

I am proud to have been born and raised in a humble background in Bangladesh, a third-world country where access to quality education is a luxury. Despite these challenges, I have been able to succeed academically and have been accepted into the prestigious Islamic University of Technology in Bangladesh, where I was ranked 195th in the national admission exam. This is a highly competitive institution and I am honored to have been selected among a talented pool of applicants.

I am confident that the curriculum and Professor X's guidance at Carnegie Mellon will provide me with the knowledge and skills necessary to make a significant contribution to the field of cybersecurity. My thesis project on automated exploit generation has given me hands-on experience in the field and a deeper understanding of the challenges businesses face in protecting their systems and data from cyberattacks. These experiences have only served to further fuel my motivation to stay up to date with the latest developments in the field and continuously innovate in order to make a positive impact.

In addition to my academic achievements, I have honed my problem-solving and teamwork skills through my participation in capture the flag contests and other extracurricular activities. These experiences have emphasized the importance of cooperation and communication in the cybersecurity industry, skills that I believe will serve me well as a graduate student at Carnegie Mellon.

In conclusion, I am deeply motivated and excited about the opportunity to study at Carnegie Mellon University and work with Professor X. I believe that my academic background, hands-on experience, and commitment to the field make me an excellent candidate for the Master's degree in cybersecurity. I am eager to bring my skills, knowledge, and passion to the program and eventually, to the industry. I am confident that the education and training I will receive at Carnegie Mellon will prepare me to make a meaningful impact in the field of cybersecurity and bring my humble background to the forefront in a positive way.

\end{document}

