\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
% \usepackage{fontspec}
\usepackage{color}
\usepackage{ragged2e}
% \setmainfont{Montserrat}

\title{Life Long Learning}
\author{Tasnimul Hasnat \\190041113}
\date{\today}

\begin{document}
\maketitle
% \section{Introduction}
\emph{Lifelong learning} is the ongoing process of learning and acquiring new skills and knowledge throughout one's life. It's important for a number of reasons.

First, the world is constantly changing, and technology is advancing at an exponential rate. To keep up with these changes and stay competitive in the job market, it's important to continuously learn and adapt. Lifelong learning helps individuals stay current and relevant in their careers, and can also help them pursue new opportunities and advancements.

Second, lifelong learning can help individuals stay engaged and fulfilled in their personal and professional lives. By constantly learning and growing, individuals can stay motivated and challenged, which can lead to a greater sense of purpose and satisfaction.

Third, lifelong learning can also have positive impacts on mental and physical health. Engaging in educational activities has been linked to improved cognitive function and mental well-being, as well as a reduced risk of developing certain chronic conditions.

There are many ways to engage in lifelong learning, including taking classes, reading books and articles, attending lectures and workshops, and participating in online courses and MOOCs (massive open online courses). It's never too late to start learning, and the benefits of lifelong learning are numerous and far-reaching.

In conclusion, lifelong learning is an essential component of personal and professional development. It helps individuals stay current and relevant in their careers, stay engaged and fulfilled in their lives, and can have positive impacts on mental and physical health. Whether through formal education or self-guided learning, there are endless opportunities for individuals to continue learning and growing throughout their lives.
And as all ways follow this teaching,
\begin{quote}
\textcolor{red}{\textit{\textbf{``Learning is a treasure that will follow its owner everywhere."}}}
\begin{flushright}
 \raggedleft\textcolor{red}{\textbf{\textit{--Chinese Proverb}}}
\end{flushright}
\end{quote}
\end{document}
